Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-21 WSSSPE1_report/WSSSPE1_summary_report.tex
Adds closing recommendation to define sustainability.

Finally, in the workshop's closing session, one of the discussion topics was
what success would look like for the set of WSSSPE activities beyond just the workshop.
One of the answers that was suggested was
having an agreed version of what we mean by sustainability.

@@

>>>>

@@

One of the subjects that contributed papers, attendees, and speakers
wrestled with repeatedly is defining sustainability such that the
community can get behind it. Although some had hoped that at least an
initial consensus could be reached in the course of the workshop, this
proved elusive. However, in the absence of such a definition it will
remain difficult to define exactly what the goals should be towards
achieving, or even only improving software sustainability, and hence
what practices should be followed and implemented when. Thus, to be
seen successful, activities emerging from or following this first
WSSSPE workshop should include working out a community consensus on
what we mean by sustainability.
